---
title: "MADRID GROUP"
author: "DEFACTO"
date: 'October 15th - October 17th'
output:
 
  html_document:
    css: FORMATO.css
    highlight: textmate
    theme: cosmo
    toc: yes
    toc_float: yes
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(readxl)
library(dplyr)
library(knitr)
library(timevis)

```

## Accommodation

### _**Hotel Ilunion Atrium**_

<iframe src="HOTEL ILUNION ATRIUM/IlunionAtrium.html" frameborder="0" width="100%" height="1050" scrolling="no"></iframe>

## MAP

<iframe src="https://www.google.com/maps/d/u/0/embed?mid=1hdpA1TbVLt7qmNjZLVZCDCYWUSnv6-Hc" width="100%" height="480"></iframe>

*****

## Budget

<iframe src="https://plm20190012budget.netlify.com/"  frameborder="0" width="100%" height="600" scrolling="no"></iframe>

<br>

## Terms & Conditions

  * Rates valid for 2019.
  
  * Net rates for Defacto
  
  * For a group of minimum 10 pax.
  
  * Cutting Edge Events management fee including in the detailed rates
  
  * VAT included. 
  
  * No reservation has been done. Availability upon request.
  
  * Costs for train Madrid - Valencia can change

## Amaze your clients!!

<div class="client_offer">

<p>Didn't you just love our presentation ? Our first goal here at _**Cutting Edge Events**_ is to help you **win** this business. You will most likely now collate the information contained in this website and make your own presentation
to show your client<br>

<p>Why not leverage our technology, and present your client with the same format ? As a **totally free service**, we offer you the possibility of doing the work for you</p>

<p> We will: 
  <ul>
    * Follow your instructions to add anything you want to be in your presentation, and delete anything that you don't consider relevant
    * Include your logo and company details, and remove all our company details
    * We can even change some colors to mimic your corporate identity
    * We will send you the new link, and it will look as if it was your work
  </ul>
</p>
</div>

<style>

.client_offer{
background-color: blue;
color: white;
padding: 10px;
border: 1px solid black;
margin-left: 25px;
border-radius: 5px;
font-style: italic;
}
</style>

******************




